Grove: A Bidirectionally Typed Collaborative Structure Editor Calculus

### 2024-11-22 sections/discussion-and-conclusion.tex
directory restructuring and hiding appendices
add artifact citation

Although our focus was on tree editing, some aspects of a program are more naturally linearly structured, e.g. string literals. We also leave to future work the problem of combining existing work on sequence CRDTs~\cite{ahmed2011evaluating,kleppmann2020moving} with our work on tree/graph CRDTs.

@@

>>>>

Although our focus was on tree editing, some aspects of a program are more naturally linearly structured, e.g. string literals. We also leave to future work the problem of combining existing work on sequence CRDTs with our work on tree/graph CRDTs.

@@

\section*{Data Availability Statement}
The artifact \cite{grove-artifact} that accompanies this work contains the Agda mechanization of the theorems discussed in section~\ref{sub:marking-agda} and section~\ref{sec:formalism-agda} and contains the implementation of the Grove Workbench discussed in section~\ref{sec:Implementation}.

### 2024-11-22 sections/formalism.tex
add artifact citation

\subsection{Mechanized Metatheory}

The definitions and theorems in \autoref{sub:Convergent Graphs} and \autoref{subsub:Graph Decomposition} have been mechanized in the Agda proof assistant, with the exception that termination is justified separately for some definitions and proofs. In particular, \autoref{thm:Commutativity} and \autoref{thm:Recomposability} are formalized and proven. \autoref{lem:uniq-classification} follows from the more powerful theorem of classification correctness and completeness, which is mechanized and used to prove \autoref{thm:Recomposability}.

>>>>

\subsection{Mechanized Metatheory}
\label{sec:formalism-agda}

The definitions and theorems in \autoref{sub:Convergent Graphs} and \autoref{subsub:Graph Decomposition} have been mechanized~\cite{grove-artifact} in the Agda proof assistant, with the exception that termination is justified separately for some definitions and proofs. In particular, \autoref{thm:Commutativity} and \autoref{thm:Recomposability} are formalized and proven. \autoref{lem:uniq-classification} follows from the more powerful theorem of classification correctness and completeness, which is mechanized and used to prove \autoref{thm:Recomposability}.

### 2024-11-22 sections/marking-system.tex
add artifact citation

We have mechanized our extension of the marked lambda calculus and these metatheorems using the Agda proof assistant, taking the standard approach of modeling judgments as inductive datatypes and inference rules as constructors. Marked terms are intrinsically typed, allowing $L$ to be computed as a function of the term.

>>>>

We have mechanized~\cite{grove-artifact} our extension of the marked lambda calculus and these metatheorems using the Agda proof assistant, taking the standard approach of modeling judgments as inductive datatypes and inference rules as constructors. Marked terms are intrinsically typed, allowing $L$ to be computed as a function of the term.
